Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-05-13 hpmoon-asoco.tex
Adds clarification in the problem description section rev #4

This subsection describes the quality indicators used and the experimental setup. The chosen quality indicators are:

\begin{itemize}
\item Hypervolume (HV): measures the area formed by all non-dominated solutions found with respect to a reference point. Higher values imply better quality of the PF. Figure \ref{fig:hypervolume} clarifies how the hypervolume is calculated.
\item Inverted Generational distance (IGD): calculates the distance of the obtained set of solutions to the optimal PF. Therefore, this metric requires the optimal PF found in the literature, or the theoretical one. In this metric, the lower the better. %Pablo: theoretical?
\item Spread (S): Measures the spread between solutions, taking into account the Euclidean distance between consecutive solutions. As in previous metric, the lower the value, the better, as it implies solutions distributed along all the PF.
\end{itemize}

@@

Those metrics \textcolor{blue}{have been chosen} not only because they have been used
extensively, especially in some of the papers presented in Section \ref{sec:soa}
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
but also because they cover different quality criteria. Mathematical
formulation of these metrics can be found in
\cite{Dorronsoro13superlinear}.

@@

ZDT \citep{zdt2000a} has been chosen as a benchmark, since it is the
most widely used in this area
\citep{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}. This
benchmark includes several functions, with different features that are
representative of real-world optimization problems. Mathematical
formulation of each function is available in \citep{zdt2000a}.

>>>>

% Some introduction. ... We will describe here the design of the
% experiments bla bla bla--- JJ

This subsection describes the \textcolor{blue}{measurements of
  quality} used \textcolor{blue}{; these are}:

% Justify this - JJ
\begin{itemize}
\item Hypervolume (HV): measures the area formed by all non-dominated solutions found with respect to a reference point. Higher values imply better quality of the PF. Figure \ref{fig:hypervolume} clarifies how the hypervolume is calculated.
\item Inverted Generational distance (IGD): calculates the distance of the obtained set of solutions to the optimal PF. Therefore, this metric requires the optimal PF found in the literature, or the theoretical one. In this metric, the lower the better. %Pablo: theoretical?
\item Spread (S): Measures the spread between solutions, taking into account the Euclidean distance between consecutive solutions. As in previous metric, the lower the value, the better, as it implies solutions distributed along all the PF.
\end{itemize}

@@

% Move this to the top - JJ
Those metrics \textcolor{blue}{have been chosen} not only because they have been used
extensively, especially in some of the papers presented in Section \ref{sec:soa}
\cite{Dorronsoro13superlinear,Durillo08masterslave,Hiroyasu07discussion,Wang09parallel,Martens13asynchronous},
but also because they cover different quality criteria. Mathematical
formulation of these metrics can be found in
\cite{Dorronsoro13superlinear}.

@@

ZDT \citep{zdt2000a} has been chosen as a benchmark, since it is the
most widely used in this area
\citep{Deb03distributed,Martens13asynchronous,Wang09parallel,Durillo08masterslave}. This
benchmark includes several functions, with different features that are
representative of real-world optimization problems. Mathematical
formulation of each function is available in \citep{zdt2000a}. \textcolor{blue}{Please
note that the ZDT problems are non-epistatic, so in principle our
conclusions should be extensible only to multiobjective problems with
the same nature.}
